---
title: "Senior Thesis"
subtitle: 'Conceptualizing Death: How Individual Differences Influence Belief in the
  Afterlife'
output: html_document
---

```{r setup, echo=FALSE, message=FALSE}
library(knitr)
library(plyr)
library(dplyr)
library(ggplot2)
library(stats)
library(xtable)
read_chunk("adult_lm.R")
```

***
### Irene Jea
<br>


## **Where did my data come from?**
***
Using a combination of online questionnaires and in-person interviews, I *painstakingly* collected data from 114 participants over the course of several months. 

The resulting demographic information, political/religious beliefs, and afterlife belief scores are stored in the accompanying CSV file.

<br>

## **What libraries were used?**
***
- **stats**: needed to calculate correlations and perform regression analysis
- **plyr and dplyr**: used to clean and organize data
- **ggplot2**: plotting
- **xtable**: saves a lot of frustration when formatting LaTeX tables

<br>

## **Preparing the data**
***
```{r echo=FALSE}
<<get_data>>
```

#### Decide which variables to include
I completed my study having collected `r ncol(afterlife.data)` measures. In hindsight, however, many don't play into a person's afterlife belief. I only want to incorporate variables that are relevant/important (backed by research, theories, etc.). 
<br>

```{r}
<<prepare_data>>
```
<br>

#### What's left are the measures I believe are the best predictors for afterlife belief.
```{r message=FALSE, echo=FALSE}
colnames(afterlife.adultdata)
```
<br>

#### Check for multicollinearity and get rid of offenders.

<br>

Religious Behavior needs to go

```{r echo=FALSE, message=FALSE}
ggplot(afterlife.adultdata, aes(x=ReligiousBehavior_Score, y = ReligiousFund_Score)) + geom_point()
```
r = `r cor(afterlife.adultdata$ReligiousBehavior_Score, afterlife.adultdata$ReligiousFund_Score)`

<br>

Religious Commitment needs to go

```{r echo=FALSE, message=FALSE}
ggplot(afterlife.adultdata, aes(x=ReligiousCommit_Score, y = ReligiousFund_Score)) + geom_point()
```
r = `r cor(afterlife.adultdata$ReligiousCommit_Score, afterlife.adultdata$ReligiousFund_Score)`
<br>
<br>

#### Here I realize that my data is regrettably sparse. I need to modify some of the variable groups so they are less specific.

```{r}
<<mutate_var>>  
```
<br>

#### Data is ready! Variables to include in model:

```{r include=FALSE}
<<corr>>
```
```{r echo=FALSE}  
colnames(afterlife.adultdata)
```

<br>

## **Building the regression models**
***
#### My study involved a priming condition, so I want to compare a model that accounts for prime interactions with one that does not.
<br>

```{r message=FALSE, echo=FALSE}
<<lm>>
```

<br>

#### xtable works wonders for converting R tables into LaTeX format

```{r}
<<xtable>>
<<print>>
```




